---
title: "A Small Reproducible R Report"
author: ""
date: "`r Sys.Date()`"
output: github_document
---

This report shows how Markdown text, R code, tables, and plots can live together. It uses R's built-in `iris` dataset.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.width = 7, fig.height = 5)
set.seed(42)
library(dplyr)
library(ggplot2)
```

## Inspect the data

```{r inspect}
head(iris)
summary(iris)
```

## Summarize by group

```{r summary}
species_summary <- iris |>
  group_by(Species) |>
  summarise(
    n = n(),
    mean_petal_length = mean(Petal.Length),
    sd_petal_length = sd(Petal.Length),
    .groups = "drop"
  )
species_summary
```

## Plot the observations

```{r plot}
ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point(size = 2) +
  labs(title = "Iris measurements",
       x = "Sepal length", y = "Petal length") +
  theme_minimal()
```

## Fit a simple model

```{r model}
fit <- lm(Petal.Length ~ Sepal.Length + Species, data = iris)
summary(fit)
```

The report is only as reproducible as its source data, code, package versions, and analysis decisions. For an important project, record `sessionInfo()` in an appendix or a separate text file.

```{r session, echo=FALSE}
sessionInfo()
```
